The Efficient Handling of Guards \\in the Design of RPython's Tracing JIT

### 2012-08-17 talk/vmil2012/paper.tex
(cfbolz, leuschel): some tweaks to the introduction and abstract

\begin{abstract}
Tracing just-in-time (JIT) compilers record linear control flow paths,
inserting operations called guards at points of possible divergence. These
operations occur frequently in generated traces and therefore it is important to
design and implement them carefully to find the right trade-off between
execution speed, deoptimization,
and memory overhead.  In this paper we describe the design decisions about
guards taken in the implementation of the RPython tracing JIT. Furthermore we
measure various properties of guards.
% \o/
\end{abstract}

@@

Our aim is to help understand the constraints when implementing guards
and to describe the concrete techniques used in the various layers of RPython's
tracing JIT. All design decisions will be motivated by concrete numbers for the
frequency and the overhead related to guards.

>>>>

\begin{abstract}
Tracing just-in-time (JIT) compilers record linear control flow paths,
inserting operations called guards at points of possible divergence. These
operations occur frequently in generated traces and therefore it is important to
design and implement them carefully to find the right trade-off between
execution speed, deoptimization,
and memory overhead. In this paper, we perform an empirical analysis of runtime
properties of guards. This is used to guide the design of guards in the RPython
tracing JIT.
% \o/
\end{abstract}

@@

Our aim is to help understand the constraints when implementing guards
and to describe the concrete techniques used in the various layers of RPython's
tracing JIT. All design decisions are be motivated by an empirical analysis of the
frequency and the overhead related to guards.
